### 2025-01-02 sections/4-results.tex
wip: updating table and plots

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/fashion-mnist-60000.png}\\
        \subcaption{Fashion-mnist}
        \label{fig:results:fashion-mnist-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/glove-25-1183514.png}\\
        \subcaption{Glove-25}
        \label{fig:results:glove-25-lfd}
    \end{subfigure}
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/sift-1000000.png}\\
        \subcaption{Sift}
        \label{fig:results:sift-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/radio-ml-97920.png}\\
        \subcaption{RadioML}
        \label{fig:results:radioml-lfd}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/silva-2224640.png}\\
        \subcaption{Silva 18S}
        \label{fig:results:silva-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/random-1000000.png}\\
        \subcaption{A random dataset}
        \label{fig:results:random-lfd}
    \end{subfigure}
    \vspace{1em}
    \caption{Local fractal dimension vs. cluster depth across six datasets, grouped by decile of local fractal dimension and weighted by the cardinalities of the clusters.
    The last dataset is randomly generated.}
    \label{fig:results:lfd-plots}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/fashion-mnist-knn-10.png}
        \subcaption{Fashion-Mnist for $k=10$.}
        \label{fig:results:fashion-mnist-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/glove-25-knn-10.png}
        \subcaption{Glove-25 for $k=10$.}
        \label{fig:results:glove-25-scaling}
    \end{subfigure}%
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/sift-knn-10.png}
        \subcaption{Sift for $k=10$.}
        \label{fig:results:sift-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/radio-ml-knn-10.png}
        \subcaption{RadioML for $k=10$ at SnR = 10dB.}
        \label{fig:results:radioml-scaling}
    \end{subfigure}%
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/silva-knn-10.png}
        \subcaption{Silva for $k=10$.}
        \label{fig:results:silva-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/random-knn-10.png}
        \subcaption{A random dataset for $k=10$.}
        \label{fig:results:random-scaling}
    \end{subfigure}%
    \caption{Throughput across six datasets, including a randomly-generated dataset.
    In each plot, the horizontal axis represents increasing cardinality of the dataset, while the vertical axis represents the throughput in queries per second (higher is better).
    Note that for RadioML, all three algorithms performed nearly identically, so distinct lines are not visible.
    For some algorithms, we were not able to take measurements for each cardinality because the index-building required more RAM than was available (i.e. more then 512GB).}
    \label{fig:results:scaling-plots}
\end{figure}

@@

        \begin{tiny}
            \begin{sc}
                \begin{tabular}{|c|l|p{1.2cm}|p{0.9cm}|p{1.2cm}|p{0.9cm}|p{1.2cm}|p{0.9cm}|p{1.2cm}|p{0.9cm}|}

@@

                    & \multirow{2}{*}{\textbf{Multiplier}} & \multicolumn{2}{|c}{\textbf{hnsw}} & \multicolumn{2}{|c}{\textbf{annoy}} & \multicolumn{2}{|c}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{cakes}} \\\cline{3-10}

@@

                    & 1   & 1.33~$\times10^{4}$ & 0.954  & 2.19~$\times10^{3}$ & 0.950  & 2.01~$\times10^{3}$ & 1.000* & 2.17~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 2   & 1.38~$\times10^{4}$ & 0.803  & 2.12~$\times10^{3}$ & 0.927  & 9.39~$\times10^{2}$ & 1.000* & 1.14~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 4   & 1.66~$\times10^{4}$ & 0.681  & 2.04~$\times10^{3}$ & 0.898  & 4.61~$\times10^{2}$ & 0.997  & 9.82~$\times10^{2}$ & 1.000  \\\cline{2-10}
                    & 8   & 1.68~$\times10^{4}$ & 0.525  & 1.93~$\times10^{3}$ & 0.857  & 2.26~$\times10^{2}$ & 0.995  & 1.18~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 16  & 1.87~$\times10^{4}$ & 0.494  & 1.84~$\times10^{3}$ & 0.862  & 1.17~$\times10^{2}$ & 0.991  & 1.20~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 32  & 1.56~$\times10^{4}$ & 0.542  & 1.85~$\times10^{3}$ & 0.775  & 5.91~$\times10^{1}$ & 0.985  & 1.16~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 64  & 1.50~$\times10^{4}$ & 0.378  & 1.78~$\times10^{3}$ & 0.677  & 2.61~$\times10^{1}$ & 0.968  & 1.10~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 128 & 1.49~$\times10^{4}$ & 0.357  & 1.66~$\times10^{3}$ & 0.538  & 1.33~$\times10^{1}$ & 0.964  & 1.04~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 256 & --                  & --     & 1.60~$\times10^{3}$ & 0.592  & 6.65~$\times10^{0}$ & 0.962  & 1.06~$\times10^{3}$ & 1.000  \\\cline{2-10}
                    & 512 & --                  & --     & 1.83~$\times10^{3}$ & 0.581  & 3.56~$\times10^{0}$ & 0.949  & 1.04~$\times10^{3}$ & 1.000  \\

@@

                    & 1   & 2.28~$\times10^{4}$ & 0.801 & 2.83~$\times10^{3}$ & 0.835 & 2.38~$\times10^{3}$ & 1.000* & 7.22~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 2   & 2.38~$\times10^{4}$ & 0.607 & 2.70~$\times10^{3}$ & 0.832 & 1.19~$\times10^{3}$ & 1.000* & 5.75~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 4   & 2.50~$\times10^{4}$ & 0.443 & 2.61~$\times10^{3}$ & 0.839 & 6.19~$\times10^{2}$ & 1.000* & 6.25~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 8   & 2.78~$\times10^{4}$ & 0.294 & 2.51~$\times10^{3}$ & 0.834 & 3.03~$\times10^{2}$ & 1.000* & 5.93~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 16  & 3.11~$\times10^{4}$ & 0.213 & 2.23~$\times10^{3}$ & 0.885 & 1.51~$\times10^{2}$ & 1.000* & 5.49~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 32  & 3.24~$\times10^{4}$ & 0.178 & 2.01~$\times10^{3}$ & 0.764 & 7.40~$\times10^{1}$ & 0.999  & 4.75~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 64  & --                  & --    & 1.99~$\times10^{3}$ & 0.631 & 3.77~$\times10^{1}$ & 0.997  & 4.61~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 128 & --                  & --    & --                  & --    & 1.90~$\times10^{1}$ & 0.998  & 4.41~$\times10^{2}$ & 1.000* \\\cline{2-10}
                    & 256 & --                  & --    & --                  & --    & 9.47~$\times10^{0}$ & 0.998  & 4.23~$\times10^{2}$ & 1.000* \\

@@

                    & 1   & 1.93~$\times10^{4}$ & 0.782 & 3.98~$\times10^{3}$ & 0.686 & 6.98~$\times10^{2}$ & 1.000* & 5.52~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 2   & 2.03~$\times10^{4}$ & 0.552 & 3.80~$\times10^{3}$ & 0.614 & 3.30~$\times10^{2}$ & 1.000* & 2.66~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 4   & 2.18~$\times10^{4}$ & 0.394 & 3.69~$\times10^{3}$ & 0.637 & 1.65~$\times10^{2}$ & 1.000* & 1.43~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 8   & 2.48~$\times10^{4}$ & 0.298 & 3.58~$\times10^{3}$ & 0.710 & 7.72~$\times10^{1}$ & 1.000* & 7.94~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 16  & 2.68~$\times10^{4}$ & 0.210 & 3.50~$\times10^{3}$ & 0.690 & 3.98~$\times10^{1}$ & 1.000* & 8.12~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 32  & 2.75~$\times10^{4}$ & 0.193 & 3.44~$\times10^{3}$ & 0.639 & 2.09~$\times10^{1}$ & 0.999  & 7.81~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 64  & --                  & --    & 3.39~$\times10^{3}$ & 0.678 & 8.87~$\times10^{0}$ & 0.997  & 7.43~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 128 & --                  & --    & 3.36~$\times10^{3}$ & 0.643 & 4.78~$\times10^{0}$ & 0.993  & 6.80~$\times10^{1}$ & 1.000 \\

@@

                    & 1  & 1.17~$\times10^{4}$ & 0.060 & 4.28~$\times10^{3}$ & 0.028 & 7.34~$\times10^{2}$ & 1.000* & 5.54~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 2  & 1.01~$\times10^{4}$ & 0.048 & 4.04~$\times10^{3}$ & 0.021 & 3.58~$\times10^{2}$ & 1.000* & 2.69~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 4  & 9.12~$\times10^{3}$ & 0.031 & 3.64~$\times10^{3}$ & 0.014 & 1.90~$\times10^{2}$ & 1.000* & 1.37~$\times10^{2}$ & 1.000 \\\cline{2-10}
                    & 8  & 8.35~$\times10^{3}$ & 0.022 & 3.37~$\times10^{3}$ & 0.013 & 8.84~$\times10^{1}$ & 1.000* & 5.69~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 16 & 8.25~$\times10^{3}$ & 0.008 & 3.17~$\times10^{3}$ & 0.006 & 4.36~$\times10^{1}$ & 1.000* & 2.61~$\times10^{1}$ & 1.000 \\\cline{2-10}
                    & 32 & --                  & --    & 3.01~$\times10^{3}$ & 0.007 & 1.72~$\times10^{1}$ & 1.000* & 1.35~$\times10^{1}$ & 1.000 \\

@@

            \end{sc}
        \end{tiny}

>>>>

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/fashion-mnist-60000.png}\\
        \subcaption{Fashion-mnist}
        \label{fig:results:fashion-mnist-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/glove-25-1183514.png}\\
        \subcaption{Glove-25}
        \label{fig:results:glove-25-lfd}
    \end{subfigure}
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/sift-1000000.png}\\
        \subcaption{Sift}
        \label{fig:results:sift-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/random-1000000.png}\\
        \subcaption{A random dataset}
        \label{fig:results:random-lfd}
    \end{subfigure}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/radio-ml-97920.png}\\
        \subcaption{RadioML}
        \label{fig:results:radioml-lfd}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{images/lfd/silva-2224640.png}\\
        \subcaption{Silva 18S}
        \label{fig:results:silva-lfd}
    \end{subfigure}%
    \vspace{1em}
    \caption{Local fractal dimension vs. cluster depth across six datasets, grouped by decile of local fractal dimension and weighted by the cardinalities of the clusters.
    The last dataset is randomly generated.}
    \label{fig:results:lfd-plots}
\end{figure}

@@

\begin{figure}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/fashion-mnist_PermutedBall_10_throughput.png}
        \subcaption{Fashion-Mnist for $k=10$.}
        \label{fig:results:fashion-mnist-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/glove-25_PermutedBall_10_throughput.png}
        \subcaption{Glove-25 for $k=10$.}
        \label{fig:results:glove-25-scaling}
    \end{subfigure}%
    \vspace{1em}
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/sift_PermutedBall_10_throughput.png}
        \subcaption{Sift for $k=10$.}
        \label{fig:results:sift-scaling}
    \end{subfigure}%
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/sift_PermutedBall_10_throughput.png}
        \subcaption{A random dataset for $k=10$.}
        \label{fig:results:random-scaling}
    \end{subfigure}%
    \\
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/sift_PermutedBall_10_throughput.png}
        \subcaption{RadioML for $k=10$ at SnR = 10dB.}
        \label{fig:results:radioml-scaling}
    \end{subfigure}%
    \vspace{1em}
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=0.95\textwidth]{plots/sift_PermutedBall_10_throughput.png}
        \subcaption{Silva for $k=10$.}
        \label{fig:results:silva-scaling}
    \end{subfigure}%
    \caption{Throughput across six datasets, including a randomly-generated dataset.
    In each plot, the horizontal axis represents increasing cardinality of the dataset, while the vertical axis represents the throughput in queries per second (higher is better).
    Note that for RadioML, all three algorithms performed nearly identically, so distinct lines are not visible.
    For some algorithms, we were not able to take measurements for each cardinality because the index-building required more RAM than was available (i.e. more then 512GB).
    For linear search with CAKES, we only report the throughput for a few of the initial multipliers because the trend is clear.}
    \label{fig:results:scaling-plots}
\end{figure}

@@

        \begin{small}
            \begin{tabular}{|c|l|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|p{1.4cm}|p{1.0cm}|}

@@

                & \multirow{2}{*}{\textbf{Mult.}} & \multicolumn{2}{|c}{\textbf{hnsw}} & \multicolumn{2}{|c}{\textbf{annoy}} & \multicolumn{2}{|c}{\textbf{faiss-ivf}}  & \multicolumn{2}{|c|}{\textbf{cakes}} \\\cline{3-10}

@@

                & 1   & \num{1.33e4} & 0.954  & \num{2.19e3} & 0.950  & \num{2.01e3} & 1.000* & \num{3.46e3} & 1.000  \\\cline{2-10}
                & 2   & \num{1.38e4} & 0.803  & \num{2.12e3} & 0.927  & \num{9.39e2} & 1.000* & \num{3.68e3} & 1.000  \\\cline{2-10}
                & 4   & \num{1.66e4} & 0.681  & \num{2.04e3} & 0.898  & \num{4.61e2} & 0.997  & \num{3.44e3} & 1.000  \\\cline{2-10}
                & 8   & \num{1.68e4} & 0.525  & \num{1.93e3} & 0.857  & \num{2.26e2} & 0.995  & \num{3.30e3} & 1.000  \\\cline{2-10}
                & 16  & \num{1.87e4} & 0.494  & \num{1.84e3} & 0.862  & \num{1.17e2} & 0.991  & \num{3.34e3} & 1.000  \\\cline{2-10}
                & 32  & \num{1.56e4} & 0.542  & \num{1.85e3} & 0.775  & \num{5.91e1} & 0.985  & \num{2.96e3} & 1.000  \\\cline{2-10}
                & 64  & \num{1.50e4} & 0.378  & \num{1.78e3} & 0.677  & \num{2.61e1} & 0.968  & \num{3.25e3} & 1.000  \\\cline{2-10}
                & 128 & \num{1.49e4} & 0.357  & \num{1.66e3} & 0.538  & \num{1.33e1} & 0.964  & \num{2.96e3} & 1.000  \\\cline{2-10}
                & 256 & --           & --     & \num{1.60e3} & 0.592  & \num{6.65e0} & 0.962  & \num{2.79e3} & 1.000  \\\cline{2-10}
                & 512 & --           & --     & \num{1.83e3} & 0.581  & \num{3.56e0} & 0.949  & \num{2.84e3} & 1.000  \\

@@

                & 1   & \num{2.28e4} & 0.801 & \num{2.83e3} & 0.835 & \num{2.38e3} & 1.000* & \num{1.54e3} & 1.000* \\\cline{2-10}
                & 2   & \num{2.38e4} & 0.607 & \num{2.70e3} & 0.832 & \num{1.19e3} & 1.000* & \num{1.49e3} & 1.000* \\\cline{2-10}
                & 4   & \num{2.50e4} & 0.443 & \num{2.61e3} & 0.839 & \num{6.19e2} & 1.000* & \num{1.28e3} & 1.000* \\\cline{2-10}
                & 8   & \num{2.78e4} & 0.294 & \num{2.51e3} & 0.834 & \num{3.03e2} & 1.000* & \num{1.30e3} & 1.000* \\\cline{2-10}
                & 16  & \num{3.11e4} & 0.213 & \num{2.23e3} & 0.885 & \num{1.51e2} & 1.000* & \num{1.14e3} & 1.000* \\\cline{2-10}
                & 32  & \num{3.24e4} & 0.178 & \num{2.01e3} & 0.764 & \num{7.40e1} & 0.999  & \num{1.05e3} & 1.000* \\\cline{2-10}
                & 64  & --           & --    & \num{1.99e3} & 0.631 & \num{3.77e1} & 0.997  & \num{1.07e3} & 1.000* \\\cline{2-10}
                & 128 & --           & --    & --           & --    & \num{1.90e1} & 0.998  & \num{8.92e2} & 1.000* \\\cline{2-10}
                & 256 & --           & --    & --           & --    & \num{9.47e0} & 0.998  & \num{8.91e2} & 1.000* \\

@@

                & 1   & \num{1.93e4} & 0.782 & \num{3.98e3} & 0.686 & \num{6.98e2} & 1.000* & \num{6.20e2} & 1.000 \\\cline{2-10}
                & 2   & \num{2.03e4} & 0.552 & \num{3.80e3} & 0.614 & \num{3.30e2} & 1.000* & \num{2.95e2} & 1.000 \\\cline{2-10}
                & 4   & \num{2.18e4} & 0.394 & \num{3.69e3} & 0.637 & \num{1.65e2} & 1.000* & \num{1.76e2} & 1.000 \\\cline{2-10}
                & 8   & \num{2.48e4} & 0.298 & \num{3.58e3} & 0.710 & \num{7.72e1} & 1.000* & \num{1.27e2} & 1.000 \\\cline{2-10}
                & 16  & \num{2.68e4} & 0.210 & \num{3.50e3} & 0.690 & \num{3.98e1} & 1.000* & \num{1.47e2} & 1.000 \\\cline{2-10}
                & 32  & \num{2.75e4} & 0.193 & \num{3.44e3} & 0.639 & \num{2.09e1} & 0.999  & \num{1.24e2} & 1.000 \\\cline{2-10}
                & 64  & --           & --    & \num{3.39e3} & 0.678 & \num{8.87e0} & 0.997  & \num{1.34e2} & 1.000 \\\cline{2-10}
                & 128 & --           & --    & \num{3.36e3} & 0.643 & \num{4.78e0} & 0.993  & \num{1.31e2} & 1.000 \\

@@

                & 1  & \num{1.17e4} & 0.060 & \num{4.28e3} & 0.028 & \num{7.342} & 1.000* & \num{5.54e2} & 1.000 \\\cline{2-10}
                & 2  & \num{1.01e4} & 0.048 & \num{4.04e3} & 0.021 & \num{3.582} & 1.000* & \num{2.69e2} & 1.000 \\\cline{2-10}
                & 4  & \num{9.12e3} & 0.031 & \num{3.64e3} & 0.014 & \num{1.902} & 1.000* & \num{1.37e2} & 1.000 \\\cline{2-10}
                & 8  & \num{8.35e3} & 0.022 & \num{3.37e3} & 0.013 & \num{8.841} & 1.000* & \num{5.69e1} & 1.000 \\\cline{2-10}
                & 16 & \num{8.25e3} & 0.008 & \num{3.17e3} & 0.006 & \num{4.361} & 1.000* & \num{2.61e1} & 1.000 \\\cline{2-10}
                & 32 & --           & --    & \num{3.01e3} & 0.007 & \num{1.721} & 1.000* & \num{1.35e1} & 1.000 \\

@@

        \end{small}

### 2025-01-02 supplement.tex
wip: updating table and plots

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/fashion-mnist-knn-100.png}
    \caption{
        Scaling behavior of algorithms on fashion-mnist with $k=100$. 
    }
    \label{fig:supplement:fashion-mnist-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/sift-knn-100.png}
    \caption{
        Scaling behavior of algorithms on sift with $k=100$. 
    }
    \label{fig:supplement:sift-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/glove-25-knn-100.png}
    \caption{
        Scaling behavior of algorithms on glove-25 with $k=100$. 
    }
    \label{fig:supplement:glove-25-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/random-knn-100.png}
    \caption{
        Scaling behavior of algorithms on random with $k=100$. 
    }
    \label{fig:supplement:random-k-100}
\end{figure}

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/fashion-mnist_PermutedBall_100_throughput.png}
    \caption{
        Scaling behavior of algorithms on fashion-mnist with $k=100$. 
    }
    \label{fig:supplement:fashion-mnist-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/sift_PermutedBall_100_throughput.png}
    \caption{
        Scaling behavior of algorithms on sift with $k=100$. 
    }
    \label{fig:supplement:sift-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/glove-25_PermutedBall_100_throughput.png}
    \caption{
        Scaling behavior of algorithms on glove-25 with $k=100$. 
    }
    \label{fig:supplement:glove-25-k-100}
\end{figure}

\begin{figure}[ht!]
    \centering
    \includegraphics[width=3.4in]{plots/sift_PermutedBall_100_throughput.png}
    \caption{
        Scaling behavior of algorithms on random with $k=100$. 
    }
    \label{fig:supplement:random-k-100}
\end{figure}
